### 2019-08-26 Writeup/Thesis/chapters/experiments.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

\chapter{Experiments}
\label{cha:Experiments}

@@

@@

Figure \ref{tab:scallion_speed} shows the speed decline as the number of keys increases for Scallion. Any number of keys over 40 resulted in a crash for Scallion. GreenOnion's speed is almost perfectly consistent. It is slower up until  around 5 keys. This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent. In this test, the bloom filter size was kept consistent at exactly 5,000 elements.

@@

As discussed in Section \ref{exp:metric}, the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|ll|}
        \hline
        Gender & Male: & 44.44\% \\
               & Female: & 55.56\% \\
        \hline
        Age:   & 18-24: & 10.10\% \\
               & 25-29: & 20.20\% \\
               & 30-39: & 31.31\% \\
               & 40-49: & 21.21\% \\
               & 50-59: & 12.12\% \\
               & 60-69: & ~~4.04\% \\ 
               & 70-79: & ~~1.01\% \\

        \hline
        Highest Education:  
        & GCSE:                 & 13.13\% \\
        & A-Level/O-Level:      & 19.19\% \\
        & Bachelor's degree:    & 52.53\% \\
        & Master's degree:      & 13.13\% \\ 
        & PhD:                  & ~~2.02\%  \\
        \hline

@@

Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants. The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.44\% of Males to 55.56\% of Females. As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up). This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results. Further work could investigate the effect of location and dialect on similar results.

@@

Figure \ref{tab:exp1_results} shows the average results for the metrics. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

\section{Average number of near-collision keys for each metric}
\label{sec:averagePerms}
In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-matches requires computation. Table \ref{tab:average_perm} shows the average keys for each metric. The ``Compute Time'' is the computation time required for a single mid-range (2000MH/s) GPU.

@@

        \end{tabular}
    }
    \caption{Each metric's average near-collision keys}
    \label{tab:average_perm}
\end{table}

>>>>

\chapter{Experimentation Results}
\label{cha:Experiments}

@@

Figure \ref{tab:scallion_speed} shows the speed decline as the number of potential keys checked in one go increases for Scallion. Any number of keys over 40 resulted in a crash for Scallion. GreenOnion's speed is almost perfectly consistent. It is slower up until  around 5 keys. This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent. In this test, the bloom filter size was kept consistent at exactly 5,000 elements.

GreenOnion's code has been made publicly available on GitHub \footnotemark{TODO}.

@@

@@

As discussed in Section \ref{exp:metric}, the goal of the experiment was to select a set of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|ll|}
        \hline
        Gender & Male: & 44.4\% \\
               & Female: & 55.6\% \\
        \hline
        Age:   & 18-24: & 10.1\% \\
               & 25-29: & 20.2\% \\
               & 30-39: & 31.3\% \\
               & 40-49: & 21.2\% \\
               & 50-59: & 12.1\% \\
               & 60-69: & ~~4.0\% \\ 
               & 70-79: & ~~1.0\% \\

        \hline
        Highest Education:  
        & GCSE:                 & 13.1\% \\
        & A-Level/O-Level:      & 19.2\% \\
        & Bachelor's degree:    & 52.5\% \\
        & Master's degree:      & 13.1\% \\ 
        & PhD:                  & ~~2.0\%  \\
        \hline

@@

Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants. The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.4\% of Males to 55.6\% of Females. As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up). This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results. Further work could investigate the effect of location and dialect on similar results.

@@

Figure \ref{tab:exp1_results} shows the average results for the selected matches explained in Section \ref{sec:exp1_comparison}. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

\section{Average number of near-collision keys for each metric}
\label{sec:averagePerms}
In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-collision keys requires computation. Table \ref{tab:average_perm} shows the average number of potential collision keys for each metric. The ``Compute Time'' is the computation time required for a single mid-range (2000MH/s) GPU.

@@

        \end{tabular}
    }
    \caption{Each metric's average number of near-collision keys}
    \label{tab:average_perm}
\end{table}

### 2019-08-26 Writeup/Thesis/chapters/implementation.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided the functionality to present questions easily and record responses. However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality, an extra solution was required. This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically. This addition allowed the re-sampling of matches each time a user submitted a response.

\begin{figure}[!h]
  \centering
  \input{diagrams/code/GoogleAppScript.tex}
\caption{Section of code from the First Experiment's Google App Script}
\label{fig:GoogleAppScript}
\end{figure}

>>>>

\section{First Experiment}
\label{sec:exp1_implemtation}
As discussed in Section \ref{sec:matches} a list of matches were generated for each metric. Figure \ref{fig:trustwordMatch} shows the algorithm designed to compute these lists. It loads the entire Trustword dictionary and works through all combinations of words.

\begin{figure}[h!]
  \centering
  \input{code/TrustwordPlusPlus.tex}
  \caption{Main code used to generate match list}
  \label{fig:trustwordMatch}
\end{figure}

Figure \ref{fig:matchExample} further shows the code used in the \verb|leven_similar|. The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}. If this function returns true the match is added to the list of matches.

\begin{figure}[h!]
\begin{Code}[CppStyle]
bbool leven_similar(string word1, string word2)
{
  int diff = lev_distance(word1, word2);
  return diff <= DIFFERENCE_TOLERANCE;
}
\end{Code}
\caption{Example similar match function}
\label{fig:matchExample}
\end{figure}

In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided the functionality to present questions easily and record responses. However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality, an extra solution was required. This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically. This addition allowed the re-sampling of matches  each time a user submitted a response.

\begin{figure}[!h]
  \centering
  \input{code/GoogleAppScript.tex}
\caption{Section of code from the First Experiment's Google App Script}
\label{fig:GoogleAppScript}
\end{figure}

### 2019-08-26 Writeup/Thesis/code/ExponentIncrement.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

\begin{adjustbox}{width=\textwidth,height=15cm,keepaspectratio}
\begin{OpenCLCode}
///The exponent is split across two words
// i.e
//
// W[3] = XX EE EE EE
// W[4] = EE XX XX XX
//
int newExponent = get_global_id(0) + \
                    ORIGINAL_EXPONENT_VALUE;

@@

W[4] = W[4] ^ exponenetMaskRight;
\end{OpenCLCode}
\end{adjustbox}

>>>>

\begin{adjustbox}{width=\textwidth,height=15cm,keepaspectratio}
\begin{Code}[OpenCLStyle]
///The exponent is split across two words
// i.e
//
// W[3] = XX EE EE EE
// W[4] = EE XX XX XX
//
int newExponent = get_global_id(0) + \
                    ORIGINAL_EXPONENT_VALUE;

@@

W[4] = W[4] ^ exponenetMaskRight;
\end{Code}
\end{adjustbox}

### 2019-08-26 Writeup/Thesis/code/settings/OpenCL.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

\lstdefinestyle{OpenCLStyle}{
    commentstyle=\color{codegreen},
    keywordstyle={\bf \color{blue}},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left, 
    columns=fixed,                                   
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=7,
    numberstyle=\tiny, 
    numbersep=8pt,
    language=OpenCL,
}

\newtcblisting{OpenCLCode}[2][]{
	top=0cm,
	bottom=0cm,
	left=0.5cm,
	right=0cm,
	colback=white,
	colframe=black,
    arc=1pt, outer arc=1pt,
    listing only, 
    listing style=OpenCLStyle,
}

>>>>

\defineStyle{OpenCLStyle}{OpenCL}
